%% -*- coding: utf-8; -*-

\documentclass[phd,american]{ThesisPUC}

%---------- Math ----------%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bbm}
%\usepackage{ulem}
%---------- Floting ----------%
\usepackage{float}
% ---------- References ----------%
%\usepackage[sort&compress,round,comma,numbers]{natbib}
%\usepackage{natbib}
%---------- Algorithm ----------%
\input{conf_alg}
%---------- Tables ----------%
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{tabularx}
%---------- TiKz ----------%
\usepackage{threeparttable}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{psfrag,epsf}
\usepackage{multirow}
\usepackage{listings}
\usepackage{soul}
%----------citation------------%
%\usepackage{apacite}

%-----------color-----------------%
\definecolor{dkblue}{rgb}{0,0,.6}
\definecolor{turquoise}{rgb}{0.25,0.87,0.82}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{dkred}{rgb}{0.7,0,0}
\definecolor{indigo}{rgb}{0.294, 0, 0.51}
\definecolor{cyan}{rgb}{0, 0.70, 0.70}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{black}{rgb}{0,0,0}

\newcommand{\pmendes}[1]{\color{red}\textbf{paulo says: }#1\color{black}}


%\pagestyle{plain}


%Para o código em EPL
\lstdefinestyle{EPLStyle}{
  numbers=left,
  numberstyle=\footnotesize\ttfamily,
  language=SQL,
  frame=tblr,
  aboveskip=0mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{dkgreen},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3,
  %Adiciona as keywords específicas da EPL Esper
  morekeywords={after, at, context, current_timestamp,  define, distinct, every, first, grouping, grouping_id, hour, hours, initiated, inner, instanceof, irstream, is, istream, last, match_recognize,  measures, min, minute, minutes, microsecond, microseconds, millisecond, milliseconds, msec, new, offset, output, partition, pattern, rstream, sec, second, seconds, sets, some, snapshot, sql, start, terminated, then, until, usec, using, variable, weekday, when, while, window, schema},
%
  frameround=tttt,
}

\graphicspath{{images/}}

% ---------- Cover ----------%
% Adjust the advisor's title according to gender(Prof. or Prof$^{\text{a}}$.)
\author{Paulo Renato Conceição Mendes}
\authorR{Mendes, Paulo Renato Conceição}
\advisor{Sérgio Colcher}{Prof.}
\advisorR{Colcher, Sérgio}

% This thesis will use colored figures, this goes in the catalographic sheet
\usecolour{true}
\title{Spatiotemporal Localization of Actors   in Video/360-Video and its Applications}

\titleuk{Spatiotemporal Localization of Actors in Video/360-Video and its Applications}

\day{27$^{th}$}
\month{July}
\myyear{2021}

% CDD is the registry number of the area, given by the library. Our area (informatics) is 004.
\city{Rio de Janeiro}
\CDD{004}
\department{Informática}
\program{Informática}
\school{Centro Técnico Científico}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio}

%---------- Jury ----------%

% Internal jury members are declared with \jurymember{name}{title}{department}{university}
% external jury members are declared with \extjurymember{name}{title}{university}
\jury{
  \jurymember{Alberto Barbosa Raposo}{Prof.}{Departamento de Informática}{PUC-Rio}
  \extjurymember{Roberto Gerson de Albuquerque Azevedo}{Dr.}{Departamento de Ciência da Computação -- ETH Zurich}
  %\extjurymember{Jury 1}{Dr.}{Uni}
  % The person below is mandatory.
  % \schoolhead{Márcio da Silveira Carvalho}{Prof.}
}

%---------- Front letters ----------%
\resume
{
Bachelor's degree in Computer Science at Federal University of Maranhão (UFMA) in 2019.
}

\acknowledgment
{
\noindent
Thanks to my advisor Prof. Sérgio Colcher for his guidance and support in this journey.
Thanks to my family for the endless support.
Thanks to my friends from TeleMídia Lab, for their friendship and support. To all colleagues, faculty and staff of the PUC Rio Department of Informatics for the fellowship, learning and support.
This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
}


% Workaround for keywords. The keywords in the catalographic sheet must be separated by dots, while the ones shown in the abstract must be separated by semi-colons.
% Thats why we have two commands for each language: \keywords declares the keywords for the catalographic sheet, while \keywordsabstract declares the ones for the abstract.
\keywords
{
  \key{Clusterização}
  \key{Reconhecimento Facial}
  \key{Recomendação de Vídeo}
  \key{Vídeo 360}
  
  
}

\keywordsabstract
{
  \key{Clusterização;}
  \key{Reconhecimento Facial;}
  \key{Recomendação de Vídeo;}
  \key{Vídeo 360.}
}

\keywordsuk
{

  \key{Clustering}
  \key{Face Recognition}
  \key{Video Recommendation}
  \key{360-Video}
}

\keywordsabstractuk
{
  \key{Clustering;}
  \key{Face Recognition;}
  \key{Video Recommendation;}
  \key{360-Video.}
}

\abstract{
  A disseminação atual da IoT aumenta a implantação de soluções de processamento de fluxo de dados para monitorar e controlar elementos do mundo real. Uma dessas soluções é o Processamento de Eventos Complexos (CEP). Inicialmente, um único computador ou cluster concentraria toda a execução do CEP. No entanto, a execução centralizada do CEP não é ideal para lidar com o alto volume, velocidade e volatilidade dos fluxos de dados dos sensores IoT. Em vez disso, as aplicações CEP devem criar e decentralizar o processamento de eventos CEP, de preferência tendo agentes CEP na nuvem e em dispositivos na borda. Além disso, tão importante quanto a descentralização, é decidir como o processamento será dividido entre esses dispositivos. Dito isso, estar ciente do contexto atual de cada dispositivo, por exemplo, sua localização e sensores disponíveis, pode ajudar a coletar e (parcialmente) processar os dados em dispositivos próximos ao local onde os dados foram produzidos. Este trabalho apresenta uma plataforma de CEP distribuído com ciência de contexto chamada Global CEP Manager (GCM). GCM é um serviço do middleware ContextNet que oferece suporte à implantação e ao rearranjo dinâmico de consultas CEP baseados em contexto para motores CEP em execução na nuvem, em dispositivos na borda estacionários e M-Hubs, que são dispositivos na borda móveis do ContextNet. O GCM usa o ContextMatcher, que também faz parte deste trabalho. ContextMatcher é um módulo para aplicações ContextNet que permite a entrega de mensagens para nós cujo contexto esteja de compatível com um determinado conjunto de características contextuais.
}

\abstractuk{
  The current dissemination of IoT increases the deployment of stream processing solutions for monitoring and controlling elements of the real world. One of those solutions is Complex Event Processing (CEP). Initially, a single computer/cluster would concentrate all the CEP execution. However, a centralized execution of CEP is not suitable for coping with the high volume, velocity, and volatility of IoT sensors’ data streams. Instead, applications using CEP should deploy a distributed CEP Event Processing Network, preferably having CEP agents both in the cloud and at edge devices. Also, deciding the arrangement used to split the processing among these tiers and their devices can be just as important. That said, being aware of each of the devices’ current context, for instance, their location and available sensors, can help to collect and (partially) process the data on devices close to the data’s production site. This work presents a context-aware distributed CEP platform called Global CEP Manager (GCM). GCM is a service of the ContextNet middleware that supports the context-based deployment, and dynamic rearrangement of CEP queries to CEP engines executing in the cloud, stationary edge devices, and  M-Hubs, which are ContextNet’s mobile edge devices. GCM uses the ContextMatcher, which is also part of this work. ContextMatcher is a module for ContextNet applications that enables the delivery of messages for nodes that match a specified set of contextual requirements.
}


% WARNING
% The epigraph, if present, must come before the first chapter, always.
% There is a list of abreviations (abrevs.tex) which is included automatically in the ThesisPUC.cls, and is optional, comment the \include{abrevs} line if you do not wish to included it.
% Rationale: In the original template, the list of abreviations came before the epigraph, which caused problems with the university library, thus I've included it in the cls file.
% TODO: Declare a boolean option in the ThesisPUC.cls class in order to selectively include the abreviations list.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\input{chapters/01_Introduction}
\input{chapters/02_Related}
\input{chapters/03_video_face_clustering}
\input{chapters/04_face_recognition}
\input{chapters/05_educational_recommendation}
\input{chapters/06_automatic_subtitles}
\input{chapters/Conclusions}

\arial
\bibliography{references}

% Apendix chapters below.
%\normalfont
%\appendix
%\input{appendix.tex}

\bibliographystyle{bibstyles/IEEEtran}

\end{document}